---
title: Car Analysis
author: ~
date: '2017-06-05'
slug: car-analysis
categories: []
tags: []
description: 'A classification of cars'
---
#Welcome

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

Welcome to my first blog post! This is a walkthrough of R markdown using the base R mtcars dataframe. The following 5 cars were randomly generated using this code.

```{r mtcars, include=TRUE}
mtcars[runif(5,min=1,max=20),]
```
##Hypothesis

My basic hypothesis is that car manufacturers seek to maximize all available technology. This implies that the power to weight ratio of cars with similar engine specifications should consistently hit a maximum asymptote. Let us test that hypothesis using engine cylinder as a proxy for engine limitations.

```{r, include = TRUE}
ggplot(data=mtcars, aes(x=wt, y=hp)) +
  geom_point(alpha=0.5) +
  facet_wrap(~cyl) +
  geom_smooth(method=lm)

```

As can be observed, the hypothesis has been disproved. There is too much scattering to suggest that the line of best fit in this diagram represents a maximum production possibility frontier. Instead, manufacturers are probably optimising to fit specific clientele rather than pushing a technological limit.